\markdownRendererHeadingOne{Research and History}\markdownRendererInterblockSeparator
{}\markdownRendererHeadingTwo{Psychoanalytic Approach}\markdownRendererInterblockSeparator
{}\markdownRendererUlBeginTight
\markdownRendererUlItem Very influenced by Sigmeund Freud.\markdownRendererUlItemEnd 
\markdownRendererUlItem In the late 1800s, he came up with a psychoanalytic approach which was about the unconscious drives.\markdownRendererUlItemEnd 
\markdownRendererUlItem For the most part, psychological approach were about drawing apart these unconscious desires.\markdownRendererUlItemEnd 
\markdownRendererUlEndTight \markdownRendererInterblockSeparator
{}\markdownRendererHeadingTwo{Behvaioral}\markdownRendererInterblockSeparator
{}\markdownRendererUlBeginTight
\markdownRendererUlItem Later, Ivan Pavlov, Skinner, Watson, theorized that you were all influenced about the ways that you were reinforced/punished.\markdownRendererUlItemEnd 
\markdownRendererUlEndTight \markdownRendererInterblockSeparator
{}\markdownRendererHeadingTwo{Humanist}\markdownRendererInterblockSeparator
{}\markdownRendererUlBeginTight
\markdownRendererUlItem Stemmed from hippies.\markdownRendererUlItemEnd 
\markdownRendererUlItem Humanist is the drive for free will.\markdownRendererUlItemEnd 
\markdownRendererUlItem You are trying to drive to reach your greatest free potential.\markdownRendererUlItemEnd 
\markdownRendererUlEndTight \markdownRendererInterblockSeparator
{}\markdownRendererBlockQuoteBegin
Mr. Rogers, isn't it a special day today
\markdownRendererBlockQuoteEnd \markdownRendererInterblockSeparator
{}\markdownRendererUlBeginTight
\markdownRendererUlItem Things like uncoditional positive regard, you are the best person to solve your own problem.\markdownRendererUlItemEnd 
\markdownRendererUlEndTight \markdownRendererInterblockSeparator
{}\markdownRendererHeadingTwo{Biological}\markdownRendererInterblockSeparator
{}\markdownRendererUlBeginTight
\markdownRendererUlItem Brain surgery, drugs, etc.\markdownRendererUlItemEnd 
\markdownRendererUlItem Your behavior is a result of neurotransmission, brain structures, etc.\markdownRendererUlItemEnd 
\markdownRendererUlItem When drugs came out, they were supposed to get people out of poor mental states.\markdownRendererUlItemEnd 
\markdownRendererUlEndTight \markdownRendererInterblockSeparator
{}\markdownRendererHeadingTwo{Cognitive}\markdownRendererInterblockSeparator
{}\markdownRendererUlBeginTight
\markdownRendererUlItem Anything about thoughts lmao\markdownRendererUlItemEnd 
\markdownRendererUlItem How do you interpret what happens.\markdownRendererUlItemEnd 
\markdownRendererUlItem This interpretation then, is going to affect your behavior. If you are getting therapy, you are probably getting cognitive behavioral therapy.\markdownRendererUlItemEnd 
\markdownRendererUlItem Ellis and Beck primarily.\markdownRendererUlItemEnd 
\markdownRendererUlEndTight \markdownRendererInterblockSeparator
{}\markdownRendererHeadingTwo{Structuralists vs Functionalists}\markdownRendererInterblockSeparator
{}\markdownRendererUlBeginTight
\markdownRendererUlItem The first two theories were structuralism and functionalism.\markdownRendererUlItemEnd 
\markdownRendererUlItem Structuralism is known to be a part of experimental psychology.\markdownRendererInterblockSeparator
{}\markdownRendererUlBeginTight
\markdownRendererUlItem Focuses on different brain elements and their capacities.\markdownRendererUlItemEnd 
\markdownRendererUlEndTight \markdownRendererUlItemEnd 
\markdownRendererUlItem Functionalism was introduced as a counter argument to structuralism.\markdownRendererInterblockSeparator
{}\markdownRendererUlBeginTight
\markdownRendererUlItem Focuses on the adaptations of human mind to different environments.\markdownRendererUlItemEnd 
\markdownRendererUlEndTight \markdownRendererUlItemEnd 
\markdownRendererUlEndTight \relax